---
title: "index.Rmd"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)  # for summary statistics and regression tables
library(magrittr)  # for 'piping': more readable code
library(ggplot2)  # the ggplot2 package provides nice function for plotting
library(interplot)  # for plotting interactions
library(dplyr)  # for data manipulation
library(devtools)
library(xlsx)
library(knitr)

```

#Introduction
The main aim of this research is to analyse whether certain variables have a substantial effect on student's ability or not. The variables that apply to this research are the follows: GDP per capita, Government expenditure, Population, Population density, Primary school pupil-teacher ratio, Mandatory schoolarisation years, Internet users and Mobile subscriptions.
Likewise, the student's ability will be analysed through three different values: math score, reading score and problem solving.

#Methodology
To analyze our research theme, we used the Data from Programme for International Student Assessment(PISA) that conducts assesment about the ......
We picked up the result of **Mathmatics, Reading and Problem Solving** that is conductet in 2012. Also, we picked the result of 2003 Problem solving as well, which is a direct assesment of life competencies that apply across different areas of the school curriculum. This data is benefitial to analyze student's ability that is not measured by academic ability.

Picked up coutries are depended on PISA data avairability,.....

Then, we have analyzed the correlation between these variables.

#Data gathering and merging process
The first dataset is from **PISA**, and the second from **the World Bank**. Both datasets are open and can be found in their respective webpages.

###Data Source
1. PISA: 
We downloaded .... and picked the following three datas up to use as dependent variables:

|Variable|Variable Name|Description|
|:--------|:------------------|:-----------------------------|
|DV|math|Mathmatics mean score(2012)|
|DV|reading|Readind mean score(2012)|
|DV|ps|Prolem Solving mean score(2012)|

2. The World Bank:
Taking aveirability into account, we picked the following variables up as explanetory variables from the World Bank Data.

|Variable|Variable Name|Description|
|:--------|:---------------|:--------------------------------|
|IV|GDPperc|GDP per Capita (current US$)|
|IV|expend|Government expenditure on education, total (% of GDP)|
|IV|pop|Population, total|
|IV|popd| Population density (people per sq. km of land area)
|IV|rteacher|Primary school pupil-teacher ratio is the average number of pupils per teacher in primary school|
|IV|eyear|Number of years that children are legally obliged to attend school|
|IV|internet|internet users (per 100 people). Internet users are individuals who have used the Internet (from any location) in the last 12 months. Internet can be used via a computer, mobile phone, personal digital assistant, games machine, digital TV etc.|
|IV|mobile|Mobile cellular subscriptions (per 100 people)|

We have cleaned and merged the relevant data of both datasets. Then, we have generate tables and figures to relate the data with the aim of addressing, as well as possible, our researching question to begin to determine whether our hypothesis is correct or not.


```{r,echo=FALSE}

```

## Multiple Regression

```{r , echo=FALSE, comment=NA, warning=FALSE, error=FALSE, message=FALSE, results='asis'}
#Regression
##Data install
data <- read.xlsx("PISA_Data.xlsx",1)

##Conducting Regression
##Math
ma.lm <- lm(math ~ log(GDPperc) + log(pop) +  popd, data=data)
ma.lm2 <- lm(math ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend, data = data)
ma.lm3 <- lm(math ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend + internet + mobile, data = data)

###Create labels
labels <- c('log(GDPperc)', 'log(pop)','popd', 'rteacher', 'eyear', 'expend', 'internet','mobile','(intercept)')

###Create table
<<<<<<< Updated upstream
stargazer(ma.lm,ma.lm2,ma.lm3, type='html',
          covariate.labels = mlabels,
          dep.var.labels = 'Math Score',
=======
stargazer(ma.lm,ma.lm2,ma.lm3, type='text',
          covariate.labels = labels,
          dep.var.labels = ('Math Score'),
          out='math_regression.txt',
          title="Table:Regression Estimates of Math Score",
          no.space=TRUE)

stargazer(ma.lm,ma.lm2,ma.lm3,
          covariate.labels = labels,
          dep.var.labels = ('Math Score'),
          title="Table:Regression Estimates of Math Score",
          type="latex", header = FALSE,
          no.space=TRUE)

stargazer(ma.lm,ma.lm2,ma.lm3, type='html',
          covariate.labels = labels,
          dep.var.labels = ('Math Score'),
          out='math_regression.html',
>>>>>>> Stashed changes
          title="Table:Regression Estimates of Math Score")
```



```{r , echo=FALSE, comment=NA, warning=FALSE, error=FALSE, message=FALSE}
###Reading
re.lm <- lm(reading ~ log(GDPperc) + log(pop) +  popd,data = data)
re.lm2 <- lm(reading ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend, data = data)
re.lm3 <- lm(reading ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend + internet + mobile,data = data)
summary(re.lm3)

stargazer(re.lm, re.lm2, re.lm3, type='text',
          covariate.labels = labels,
          dep.var.labels = ('Reading Score'),
          out='re_regression.txt',
          title="Table:Regression Estimates of Reading Score",
          no.space=TRUE)


###Problem Solving
ps.lm <- lm(ps ~ log(GDPperc) + log(pop) +  popd, data = data)
ps.lm2 <- lm(ps ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend, data = data)
ps.lm3 <- lm(ps ~ log(GDPperc) + log(pop) +  popd + rteacher + eyear + expend + internet + mobile, data = data)
summary(ps.lm3)

stargazer(ps.lm, ps.lm2, ps.lm3, type='text',
          covariate.labels = labels,
          dep.var.labels = ('Problem Solving Score'),
          out='ps_regression.txt',
          title="Table:Regression Estimates of Probleb Sloving Score",
          no.space=TRUE)

stargazer(ma.lm3, re.lm3, ps.lm3, type='text',
          covariate.labels = labels,
          out='cm_regression.txt',
          title="Table:Regression Estimates Comparison",
          no.space=TRUE)
```

##Analysis
According to the result, in the secound regressio, these variables are statistically significant.
- Math:GDP per capita
- Reading: GDP per capita, expenditure
- Problem solving: GDP per capita, population, pupills-teacher rate and duraion educational year in elementary 

In the third regression, GDP per capita is not statistically significant any more. Instead of GDP per capita, the number of internet users and population become statistically significant. 

Especially, the number of internet users is significant at 0.1% level in math and reading. We can see it bring plus effect on the both score.However, regarding the problem solving, internet is statistically significant only at 5 % level and the effect is weaker than other 2 scores.

In addition, regarding GDP per capita of math ane reading, it bring the minues effect on the both scores after the variable internet and mobile are added, though it still bring the plus effect on problem solving. Even though it is not statistically significant for math and reading, but it might possible to infere if the internet accessibility would be the same level, economically strong country's math and reading scores might be lower than economically weak countries.

Also, we noticed that about the academic ability (math and reading,) internet accessibility would bring the some impact on the scores. However, it would bring less impact on the problem solving ability.

Actually, there is some discussion that internet accessibility might bring reverse effect on student's thinkig ability. Therefore, next we focus on the problem solving score.

###Correlation between score growth
```{r,echo=FALSE}
#Growth comparison
##Data install
pisa <- read.xlsx("/Users/komaiyumi/Desktop/Social Sicence/web/PISA_Data.xlsx",2)

##Plot and Correlation
p <- ggplot(pisa, aes(Internet.users.growth, Score.growth))+geom_point()
plot(p)

growth.lm <- lm(Internet.users.growth ~ Score.growth, data=pisa)
summary(growth.lm)

```
The result shows that we cannot find any correlation between internet accessibility growth and score growth.....
